\documentclass[twoside, 12pt]{article}
\usepackage[normalem]{ulem}
\usepackage[]{fancyhdr}
\usepackage{varioref, amsmath, stmaryrd, amssymb}
\usepackage{fontspec}
\setmainfont{Corbel}[Numbers=OldStyle]
\setsansfont{Myriad Pro}[Numbers=OldStyle, Scale=MatchLowercase]
% \usepackage[oldstyle]{clara}
% \usepackage[T1]{fontenc}
\usepackage[backend=bibtex,natbib,style=authoryear,sorting=nyt]{biblatex}
\addbibresource{Bibliography.bib}
\usepackage{xcolor}
  \colorlet{arrow}{gray}
 \usepackage[colorlinks, urlcolor=blue, linkcolor=black,
  citecolor=black, filecolor=black, pagecolor=black]{hyperref}
\usepackage[norule]{footmisc}
\usepackage{microtype}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{arrows}
\usepackage[linguistics]{forest}
\usepackage[all]{nowidow}
\usepackage{gb4e}

% Better looking denotation brackets from stmaryrd
\newcommand{\denotes}[2][]{\ensuremath{\llbracket \text{#2}\rrbracket^{#1}}}

\forestset{
default preamble={for tree={s sep=5mm, inner sep=0, l=0}
}}


\newcommand{\paper}{Constructing Symmetric Predicates}


\title{\paper\thanks{Our gratitude to Gary Thoms, Satoshi Tomioka, Jason Merchant.}}
\author{Jeroen van Craenenbroeck and Kyle Johnson}
\date{\today}

% \widowpenalty=10000
% \clubpenalty=10000

\begin{document}
\raggedbottom
\begin{titlepage} 
\maketitle 
\thispagestyle{empty}
\begin{abstract}

 \noindent 
 
 \end{abstract}
 \end{titlepage} 

\thispagestyle{empty}
\noindent
There are predicates in many languages that can express a relation between individuals either by taking one plural argument referring to those individuals or two, possibly singular, arguments that together refer to those individuals. This is illustrated in (\ref{ex:external}) and~(\ref{ex:internal}).
\begin{exe}
\raggedright
\ex \label{ex:plainsymm} $aP$ $\Leftrightarrow$ $bPc$, when $a = b \oplus\ c$
\begin{xlist}
  \ex \label{ex:external} intransitive/transitive alternation
  \begin{xlist}
    \ex Arjun and Aisha dated $\Leftrightarrow$ Aisha dated Arjun
    \ex Our names rhyme $\Leftrightarrow$ Your name rhymes with mine
    \ex California and Oregon are adjacent $\Leftrightarrow$ California is adjacent to Oregon
  \end{xlist}
  \ex \label{ex:internal} transitive/ditransitive alternation
  \begin{xlist}
    \ex She mixed camphor and menthol $\Leftrightarrow$ She mixed camphor with menthol
    \ex She introduced us $\Leftrightarrow$ She introduced you to me
    \ex She combined the beans and the rice $\Leftrightarrow$ She combined the beans with the rice
  \end{xlist}
\end{xlist}
\end{exe}
Let's call these ``argument splitting alternations.'' We'll call the intransitive versions of the verbs in (\ref{ex:external}) and the transitive versions of the verbs in (\ref{ex:internal}) the ``unsplit'' variant, and the other pairs in the alternation the ``split'' variant.

\citet{Winter:2018} hypothesizes that predicates which undergo argument splitting alternations are also symmetric. A symmetric predicate is one in which the arguments, in a transitive, or the internal arguments, in a ditransitive, can be switched, preserving that component of the meaning that traces back to argument structure.
\begin{exe}
\raggedright
  \ex \label{ex:symm} $bPc$ $\Leftrightarrow$ $cPb$ (symmetric predicates)
  \begin{xlist}
  \ex \label{ex:symmtrans} Transitives
  \begin{xlist}
    \ex Aisha dated Arjun $\Leftrightarrow$ Arjun dated Aisha
    \ex Your name rhymes with my name $\Leftrightarrow$ My name rhymes with your name
    \ex California is adjacent to Oregon $\Leftrightarrow$ Oregon is adjacent to California.
  \end{xlist}
  \ex Ditransitives
  \begin{xlist}
    \ex She mixed camphor with menthol $\Leftrightarrow$ She mixed menthol with camphor 
    \ex She introduced you to me $\Leftrightarrow$ She introduced me to you
    \ex She combined the beans with the rice $\Leftrightarrow$ She combined the rice with the beans
  \end{xlist}
\end{xlist}
\end{exe}
Let's call this Winter's Generalization.\footnote{In fact, \citet{Winter:2018} argues that (\ref{ex:WL}) should be a biconditional. But he notes that there are counterexamples for the implication symmetric predicate $\rightarrow$ referential valency alternation, some of which are:
\begin{exe}
\raggedright
  \exi{(i)}
  \begin{xlist}
    \ex This resembles that. $\Leftrightarrow$ That resembles this. $\neq$ *They resemble.
    \ex She packaged this with that. $\Leftrightarrow$ She packaged that with this. $\neq$ She packaged them.
    \ex You concur with me. $\Leftrightarrow$ I concur with you $\neq$ We concur.
    \ex This compares with that. $\Leftrightarrow$ That compares with this. $\neq$ They compare.
    \ex You teamed with me. $\Leftrightarrow$ I teamed with you. $\neq$ We teamed.
  \end{xlist}
\end{exe}}
\begin{exe}
\raggedright
  \ex \label{ex:WL} Winter's Generalization\\
  If a predicate participates in an argument splitting alternation then it is symmetric.
\end{exe}
We will sketch a way of deriving Winter's Generalization that is built upon how $\theta$-roles are assigned. But we must first address what is meant when we say that two sentences have the same meaning relative to their argument structure; that is, what constitutes a symmetric predicate.

We can distinguish two classes of symmetric predicates: near symmetric and strictly symmetric. The examples in (\ref{ex:plainsymm}) are examples of strictly symmetric predicates. Near symmetric predicates are exemplified by the verbs in~(\ref{ex:nearsymm}).
\begin{exe}
\raggedright
  \ex \label{ex:nearsymm}
  \begin{xlist}
    \ex Arjun hugged Aisha. $\leftrightarrow$ Aisha hugged Arjun.
    \ex Arjun kissed Aisha. $\leftrightarrow$ Aisha kissed Arjun.
    \ex Aisha collided with Arjun. $\leftrightarrow$ Arjun collided with Aisha.
  \end{xlist}
\end{exe}
the meanings of the sentences in (\ref{ex:nearsymm}) are not strictly symmetric, as can be seen by considering the pairs in~(\ref{ex:notsymm}).
\begin{exe}
\raggedright
  \ex \label{ex:notsymm}
  \begin{xlist}
    \ex Arjun hugged the tree. $\nleftrightarrow$ \# The tree hugged Arjun.
    \ex Arjun kissed the tree. $\nleftrightarrow$ \# The tree kissed Arjun.
    \ex Aisha collided with the tree. $\nleftrightarrow$ The tree collided with Aisha.
  \end{xlist}
\end{exe}
However, in line with Winter's Generalization, the sentences in (\ref{ex:nearsymm}) can be alternative ways of expressing the meaning that the intransitive version of this verb has. In particular, when the ``$\leftrightarrow$'' relation in (\ref{ex:nearsymm}) is ``$\Leftrightarrow$,'' then these sentences express the same thing as the unsplit, intransitive, version of these verbs. The relations in (\ref{ex:nearsymmin}) hold.
\begin{exe}
% \raggedright
  \ex \label{ex:nearsymmin}
  \begin{xlist}
    \ex {} [ Arjun hugged Aisha $\Leftrightarrow$ Aisha hugged Arjun] $\rightarrow$\\ {} [Arjun and Aisha hugged $\Leftrightarrow$ Arjun hugged Aisha] 
    \ex {} [ Arjun kissed Aisha $\Leftrightarrow$ Aisha kissed Arjun] $\rightarrow$\\ {} [Arjun and Aisha kissed $\Leftrightarrow$ Arjun kissed Aisha] 
    \ex {} [ Arjun collided with Aisha $\Leftrightarrow$ Aisha collided with Arjun] $\rightarrow$\\ {} [Arjun and Aisha collided $\Leftrightarrow$ Arjun collided with Aisha] 
  \end{xlist}
\end{exe}
Near symmetric verbs obey Winter's Generalization in a contingent way, then. 

One way of thinking about this is to give to near symmetric predicates two denotations. In one, they are symmetric, and in the other they aren't. This view preserves Winter's Generalization. It claims that there is a symmetric \textit{hug}---we'll indicate this with \textit{hug_s}---whose meaning preserves the alternation in~(\ref{ex:nsymm1}).
\begin{exe}
\raggedright
  \ex \label{ex:nsymm1}
  \begin{xlist}
    \ex Arjun hugged_s Aisha $\Leftrightarrow$ Aisha hugged_s Arjun
    \ex Arjun kissed_s Aisha $\Leftrightarrow$ Aisha kissed_s Arjun
    \ex Aisha collided_s with Arjun $\Leftrightarrow$ Arjun collided_s with Aisha
  \end{xlist}
\end{exe}
The other denotation these predicates have, however, is not symmetric. Let's represent the version of these verbs with that denotation with the subscript $a$, for ``asymmetric.'' It is this version of the predicates that is found in~(\ref{ex:asymn}).
\begin{exe}
\raggedright
  \ex \label{ex:asymn}
  \begin{xlist}
    \ex Arjun hugged_a the tree. $\nLeftrightarrow$ The tree hugged_a Arjun.
    \ex Arjun kissed_a the picture. $\nLeftrightarrow$ The picture kissed_a Arjun.
    \ex Aisha collided_a with the wall. $\nLeftrightarrow$ The wall collided_a with Aisha.
  \end{xlist}
\end{exe}
These versions of the predicates are not found in the intransitive frame, and do not participate in Winter's Generalization.
\begin{exe}
\raggedright
  \ex \label{ex:asymns}
  \begin{xlist}
    \ex[\#]{Arjun and the tree hugged_a.}
    \ex[\#]{Arjun and the picture kissed_a.}
    \ex[\#]{Aisha and the wall collided_a.}
  \end{xlist}
\end{exe}

We'll argue for this view of near symmetric predicates in section yy. What it requires is an account of the relationship between the symmetric and non-symmetric versions of these predicates. If the class of predicates that have these two denotations is not arbitrary, then we should have an explanation for that class and a model of that alternation. This paper does not fill in these gaps.

Consider next the alternations in~(\ref{ex:ground1}).
\begin{exe}
\raggedright
  \ex \label{ex:ground1}
  \begin{xlist}
    \ex The string is attached to the kite. $\neq$ The kite is attached to the string.
    \ex That wire shouldn't touch the ground screw. $\neq$ The ground screw shouldn't touch that wire.
  \end{xlist}
\end{exe}
The two versions of these sentences differ in ways that have been described in terms of the figure-ground distinction familiar from gestalt psychology (\citealt{Kofka:1955}, \citealt{Talmy:1975}). The surface subjects of English sentences typically refer to the entities that the discourse is about, and this, it seems, correlates with a gestalt interpretation of the narrative being conveyed that maps it onto the ``figure.'' In the first sentence of the pairs in (\ref{ex:ground1}), the subject is more naturally the figure of the scene being described, whereas it is the object that is the figure in the second sentence of the pairs. This might be responsible for the oddness of the second member of the alternations in~(\ref{ex:ground1}). Note that the situations in which both sentences in the alternations are judged to be true are the same. We will adopt the view that the ``$\Leftrightarrow$'' relation doesn't preserve the figure-ground relationships, but does preserve truth.

Finally, consider the alternations in~(\ref{ex:agento}).
\begin{exe}
\raggedright
  \ex \label{ex:agento}
  \begin{xlist}
    \ex Aisha happily dated Arjun. $\neq$ Arjun happily dated Aisha. $\neq$ Aisha and Arjun happily dated.
    \ex Aisha willingly married Arjun. $\neq$ Arjun willingly married Aisha. $\neq$ Aisha and Arjun willingly married.
  \end{xlist}
\end{exe}
None of the sentences in these triples have the same meanings. They differ with respect to which argument of the verb is said to be happy or willing. Informally, the adverbs \textit{happily} and \textit{willingly} describe an attribute of the subject of the sentence that they are in, and the meanings in (\ref{ex:agento}) vary, therefore, by virtue of what the subject is. Importantly, what it means to be a ``subject'' for subject-oriented adverbs has to do with how the relevant argument is syntactically positioned, and not how it enters into the relation denoted by the verb. As the examples in (\ref{ex:intsadv}) show, the argument that these adverbs target can be internal arguments (in (\ref{ex:intsadv}a,b)) or even arguments of embedded clauses (in (\ref{ex:intsadv}c,d)).
\begin{exe}
\raggedright
  \ex \label{ex:intsadv}
  \begin{xlist}
    \ex[]{Aisha willingly/happily dies in the movie.}
    \ex[]{Arjun was willingly/happily examined by a doctor.}
    \ex[]{Aisha will happily/willingly appear to support Trump when he's present.}
    \ex[]{Arjun happily/willingly seems servile when it's required in Cabinet meetings.}
  \end{xlist}
\end{exe}
By contrast, these adverbs cannot modify an argument if it is not in surface subject position. In (\ref{ex:objsadv}), the adverbs cannot modify the objects, even when that object has the same, or a similar, relation to the verb that it has in~(\ref{ex:intsadv}).
\begin{exe}
\raggedright
  \ex \label{ex:objsadv}
  \begin{xlist}
    \ex Aisha killed Arjun willingly/happily.
    \ex A doctor examined Arjun willingly/happily.
  \end{xlist}
\end{exe}
Instead, the subject-oriented adverbs in (\ref{ex:objsadv}) modify the subject of these clauses. Similarly, \textit{the dog} can only be modified by a subject-oriented adverb in (\ref{ex:dog}a) where it is a surface subject.
\begin{exe}
\raggedright
  \ex \label{ex:dog}
  \begin{xlist}
    \ex The dog walked happily/willingly.
    \ex She walked the dog happily/willingly.
  \end{xlist}
\end{exe}
The subject-oriented adverbs in (\ref{ex:dog}b) can only modify \textit{she}, even though the relation \textit{the dog} bears to \textit{walk} is very similar in both these examples. We conclude that the relation ``$\Leftrightarrow$'' which symmetric predicates participate in doesn't include the meaning contributed by  subject-oriented adverbs, or other secondary predicates that relate an argument to the event being described the verb.

Let us make a note here about the meaning of these subject oriented adverbs that will become relevant shortly. While we won't give a formal semantics, we think it's clear that the relation that these adverbs have is importantly different than manner adverbs. (See \citealt{Geuder:2002} for a extensive discussion of this.) Consider, for instance, the somewhat strained interpretation that \textit{she walked the dog happily} can get when \textit{happily} is understood as a manner adverb. On this interpretation the walk that the dog is being made to endure is a happy walk. Nothing about the dog's state is communicated. A very unhappy dog could be walked in a happy manner. When \textit{happily} is subject, oriented, by contrast, it describes an attitude the subject has towards the event. In (\ref{ex:dog}a), the dog is said to be happy or willing to be the agent of walking. We make the following observation.
\begin{exe}
\raggedright
  \ex \label{ex:subjectattitude} Only surface subjects can have an attitude towards the event denoted by the VP they are the subjects of.
\end{exe}
Subject oriented adverbs live on (\ref{ex:subjectattitude}), and say something about that attitude.

What is preserved by ``$\Leftrightarrow$'' seems to be narrowly tied to the way symmetric predicates relate their arguments to the event they describe. We will follow the hypothesis that how a symmetric predicate relates their two arguments to the event have the same truth conditions no matter the order in which those arguments syntactically combine with the verb. This is what ``$\Leftrightarrow$'' means. We want an explanation for why all verbs that participate in the argument splitting alternation are verbs for which ``$\Leftrightarrow$'' holds for the different orderings of their split variant. We will also take ``$\Leftrightarrow$'' to be what holds of the split and unsplit variants of those predicates that participate in the argument splitting alternation.
\begin{exe}
\raggedright
  \ex \label{ex:rvaf} If P participates in an argument splitting alternation, then:\\ P's unsplit variant $\Leftrightarrow$ P's split variant.
\end{exe}

Winter's own explanation of Winter's Generalization invokes a set of rules from proto-predicates---logical templates for verb meanings---to lexicalizations of those proto-predicates. He takes the underlying proto-predicate to be a collective single argument predicate. There are then rules that allow that collective predicate to be expressed as a relation between individuals just in case certain conditions of similarity hold between the atoms of the argument have a certain symmetry. 

His model requires that the two-argument verbs formed from the underlying proto-predicate denote relations between arguments and an event. The denotation of transitive \textit{date}, for instance, is~(\ref{ex:marrydenW}).
\begin{exe}
\raggedright
  \ex \label{ex:marrydenW} $\lambda x\ \lambda y\ \lambda \epsilon$ \textsc{date}($x,y,\epsilon$)
\end{exe}
It is built into his explanation that verbs can be relations between entities, and indeed, characterizing the property that verbs must have to participate in Winter's Generalization as ``symmetry'' also relies on taking verbs to be relations between entities. We believe the neo-Davidsonian project of expressing the meanings of verbs in terms of $\theta$-roles is correct, however, and on that view verbs don't relate entities. Instead, entities are related to events, and not each other. The neo-Davidsonian treatment of transitive \textit{date} is~(\ref{ex:marrydenD}).
\begin{exe}
\raggedright
  \ex \label{ex:marrydenD} $\lambda x\ \lambda y\ \lambda \epsilon$ \textsc{date}($\epsilon$) $\wedge$ \textsc{agent}($y$)($\epsilon$) $\wedge$ \textsc{agent}($x$)($\epsilon$)
\end{exe}
This neo-Davidsonian view of verb denotations doesn't offer a way of expressing a symmetric relation between arguments. 

Instead, we adopt Dowty (\citeyear{Dowty:1989, Dowty:1991})'s proposal that what makes symmetric predicates (as we'll continue to call them) special is that they allow two arguments to be related to the event by the same $\theta$-role.%
%
\footnote{Winter also adopts Dowty's proposal, though he doesn't link it to his generalization.}%
%
\ Indeed, a reason for adopting Dowty's suggestion is that it explains Winter's Generalization. If arguments are related to the event described by a verb always through a $\theta$-role, and we have characterized ``$\Leftrightarrow$'' correctly, then (\ref{ex:way1}) follows.
\begin{exe}
\raggedright
  \ex \label{ex:way1} The Split Theta-role Analysis\\
  If a verb participates in the argument splitting alternation, then the $\theta$-role it assigns to its argument in the unsplit variant is the same as the $\theta$-role it assigns to the corresponding arguments in its split variant.
\end{exe}
Winter's Generalization follows from positing that the arguments in the split variant bear the same $\theta$-role, since~(\ref{ex:WRn}) is true.
\begin{exe}
\raggedright
  \ex \label{ex:WRn} If P assigns the same $\theta$-role to arguments $a$ and $b$, then $\Leftrightarrow$ is preserved in any syntax that combines $a$ and $b$ with~P.
\end{exe}
Winter's generalization, then, supports~(\ref{ex:rvadesc}).
\begin{exe}
\raggedright
  \ex \label{ex:rvadesc}
  An argument splitting alternation arises when a predicate can assign a $\theta$-role to either one or two arguments.
\end{exe}
We regard (\ref{ex:rvadesc}) to be a version of Winter's proposal. Unlike Winter's proposal, it doesn't make a claim about the relationship between proto-predicates and their lexicalizations. Instead it claims that the alternation tracks how predicates distribute their $\theta$-roles. But like Winter's proposal, it embraces the idea that how a predicate expresses the relation its arguments have to an event is where the alternation lives. In particular, it expresses the hypothesis that the ``$\Leftrightarrow$'' relation is just entailment by a $\theta$-role. The meanings preserved by ``$\Leftrightarrow$'' are just those that trace back to the meaning of a $\theta$-role. The meanings that aren't preserved by ``$\Leftrightarrow$''---like the figure/ground distinction and the information provided by subject oriented adverbs---aren't part of the meaning of a $\theta$-role. This, at any rate, is the thesis we wish to explore.

A popular alternative is to view the unsplit variant as an inherently reciprocal version of the split variant. The unsplit variants can be thought of as cases where the reciprocal arguments in (\ref{ex:recip1}b) and (\ref{ex:recip2}b) have become implicit.
\begin{exe}
\raggedright
  \ex \label{ex:recip1}
  \begin{xlist}
    \ex You are adjacent to me.
    \ex We are adjacent to each other.
  \end{xlist}
  \ex \label{ex:recip2}
  \begin{xlist}
    \ex She introduced you to me.
    \ex She introduced us to each other.
  \end{xlist}
\end{exe}
As \citet{Wehbe:2025} shows, making the reciprocal implicit causes the scope of the distributor to be very narrow, and this, in turn, makes an implicit reciprocal have subtly different meanings than the overt reciprocals. On this view, then, one can view the split variant as basic, and the unsplit version as derived from it by a process that forms an inherently reciprocal verb.%
%
\footnote{We note that taking the view that the alternation involves making normally transitive predicates reciprocal needs to be accompanied by a theory that ensures that the scope of the implicit distributor be narrower than the existential closure of the event variable to derive the effects \citet{Wehbe:2025} describes. This isn't a trivial task. Implicit arguments are often existentially closed, and when they are, the existential takes narrow scope. The mechanism for accomplishing that is different than what is required in making the distributive operator narrow. On Winter's approach, there is no distributive operator and so no problem making it narrow.}%
%
\ This gives a different characterization of near symmetric predicates than we've offered above. On the reciprocal interpretation, there is a process that takes some transitive verbs, like \textit{kiss} for instance, and makes them implicit reciprocals. Transitive \textit{kiss} can also have an overt reciprocal as object. From (\ref{ex:underkiss}), the implicit reciprocal process forms (\ref{ex:underkiss}a) and an overt reciprocal forms~(\ref{ex:underkiss}b).
\begin{exe}
\raggedright
  \ex \label{ex:underkiss} \denotes{kiss} = $\lambda x\ \lambda y\ \lambda \epsilon$ \textsc{patient}($x$)($\epsilon$) $\wedge$ \textsc{agent}($y$)($\epsilon$) $\wedge$ \textsc{kiss}($\epsilon$)
  \begin{xlist}
    \ex They_3 kissed.\\ $\exists \epsilon$ $\forall x$ [$x \in 3 \wedge \textsc{atomic}(x)$] $\rightarrow$ $\forall y$ [$y \in 3 \wedge \textsc{atomic}(y) \wedge y \neq x$] $\rightarrow$  \textsc{patient}($y$)($\epsilon$) $\wedge$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{kiss}($\epsilon$)
    \ex They_3 kissed each other.\\ $\forall x$ [$x \in 3 \wedge \textsc{atomic}(x)$] $\rightarrow$ $\forall y$ [$y \in 3 \wedge \textsc{atomic}(y) \wedge y \neq x$] $\rightarrow$\\  $\exists \epsilon$ \textsc{patient}($y$)($\epsilon$) $\wedge$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{kiss}($\epsilon$)
  \end{xlist}
\end{exe}
The central difference between these two ways of expressing \textit{kiss} is the scope of the event and the distributive operator (expressed here with universal quantifiers). Thus, for instance, (\ref{ex:underkiss}b) can describe two asymmetric relations happening at different times and locations (i.e., events). (\ref{ex:underkiss}a) can't have that interpretation since there must be a single event in which the reciprocal asymmetric kissings occur.

Our proposal, by contrast, is that the denotation of \textit{kiss} is (\ref{ex:overkiss}), which gives rise to either (\ref{ex:overkiss}a) or~(\ref{ex:overkiss}b).
\begin{exe}
\raggedright
  \ex \label{ex:overkiss} \denotes{kiss_s} = $\lambda x\ \lambda e$ \textsc{participant}($x$)($\epsilon$) $\wedge$ \textsc{kiss_s}($\epsilon$)
  \begin{xlist}
    \ex They_2 kiss.\\ $\exists \epsilon$ \textsc{participant}($3$)($\epsilon$) $\wedge$ \textsc{kiss_s}($\epsilon$)
    \
    \ex They_2 kissed each other.\\ $\forall x$ [$x \in 3 \wedge \textsc{atomic}(x)$] $\rightarrow$ $\forall y$ [$y \in 3 \wedge \textsc{atomic}(y) \wedge y \neq x$] $\rightarrow$\\  $\exists \epsilon$ \textsc{participant}($y$)($\epsilon$) $\wedge$ \textsc{participant}($x$)($\epsilon$) $\wedge$ \textsc{kiss_s}($\epsilon$)
  \end{xlist}
\end{exe}
This view requires that \textit{kiss_s} exist, and be a symmetric version of \textit{kiss_a}. 

Neither of these views are entirely problem-free. As Neu (2026) points out, the reciprocal analysis makes the wrong prediction that the implicit reciprocal should entail the overt reciprocal. And yet, the implicit reciprocal can't be used to describe many of the situations in which the overt reciprocal can. Even when there is plausibly one kissing event, as there must be with an implicit reciprocal, there is a difference between the implicit and explicit reciprocal. Imagine, for instance, that I kiss your hand while you kiss mine. This is not felicitously described with \textit{We kissed}, but is by \textit{We kissed each other}. Why this should be so is puzzling if \textit{We kissed} differs from \textit{We kissed each other} only by virtue of the scope of \textit{each}.

By contrast, Winter's analysis makes these facts less puzzling. On Winter's account, the subject of an intransitive (unsplit) \textit{kiss} refers to a group of individuals that are participants in a kissing. There is nothing transitive, or reciprocal, about it. 

The Split Theta-role Analysis, on the other hand, has the opposite problem. It requires that the split version of a truly symmetric verb be capable of substituting for an unsplit version of that verb. But Kruitwagen xxx has shown that there are systematic differences in how subjects choose these two frames. In experiments in which subjects are shown one person hugging another person who is passively accepting the embrace, there is a clear preference to use the split version of the verb rather than the unsplit version. That preference is boosted if the passive recipient of the embrace indicates, say by way of facial expression, that they have not chosen to be embraced. Moreover, when a split version of the verb is used, and the unwilling recipient of the hug is referred to be the subject, subjects strongly disprefer it. In short, what Kruitwagen xxx show is~(\ref{ex:kruittable}).
\begin{exe}
\raggedright
  \ex \label{ex:kruittable}
  \begin{xlist}
    \ex The external argument of a split symmetric predicate should be more ``agent-like'' than the internal argument of a split symmetric verb.
    \ex The external argument of a unsplit symmetric predicate should have equal ``agent-like'' properties.
  \end{xlist}
\end{exe}
What (\ref{ex:kruittable}) reflects is a general preference for mapping agent-like properties onto external arguments. For our execution of Winter's proposal, we need to separate this factor from the ``$\Leftrightarrow$'' relation. We'll make a tentative suggestion about how to do this here, but we regard this issue an unresolved problem for our proposals.

The suggestion makes use of (\ref{ex:subjectattitude}), which we saw evidence for in our examination of subject oriented adverbs.
\begin{exe}
\raggedright
  \exr{ex:subjectattitude} Only subjects can have an attitude towards the event denoted by the VP they are the subjects of.
\end{exe}
Let's assume that a VoiceP can be introduced by a functional head that relates the argument in its Specifier to the event described by the VoiceP. We'll call that head ATT.
\begin{exe}
\raggedright
  \ex \label{ex:attintro}
  \small
  \begin{forest}
  [TP
    [T [will]]
    [AttP
    [DP [Aisha, roof, name=binder ]]
    [AttP
      [Att ]
      [VoiceP
      [\textit{t}, name=trace]
        [VoiceP
          [Voice ]
          [VP
            [DP [Arjun, roof]]
            [VP
            [V [kiss]]
           ]
         ]
       ]
     ]
  ]]]
  \draw[->,>=stealth', thin, gray] (trace) to[out=south west,in=south,looseness=1] node[pos=0.75,xshift=-10mm]{} (binder);
  \end{forest}
\end{exe}
Let \denotes{Att} introduce the presupposition in (\ref{ex:preatt}) and make \denotes{AttP}=\denotes{VoiceP}.
\begin{exe}
\raggedright
  \ex \label{ex:preatt}
  $\lambda P\ \lambda x\ \forall \epsilon\ P(\epsilon) \rightarrow R(x)(\epsilon)$, where $R$ is an attitude.
\end{exe}
Subject oriented adverbs can be thought of as providing the denotation of~$R$. The goal is to let something like \textit{Aisha happily kissed Arjun} mean something like ``Aisha is happy to be the agent of kissing Arjun.'' When there is no agent oriented adverb, $R$ is a free variable, giving rise to a meaning roughly like ``There is an attitude Aisha has about being the agent of kissing Arjun.'' We suggest that ``having an attitude'' is what makes an argument more ``agent-like.'' If the movement to Specifier of AttP is A-movement, the argument that will become ``subject,'' i.e. occupy Specifier of TP, will have the attitude. That is the highest of two arguments, so generally the external $\theta$-role bearer. But, as we've seen, this argument can be an internal argument as well, as in passive or raising examples. This, we suggest, derives (\ref{ex:kruittable}).

We will pursue, then, the idea that predicates which participate in the argument splitting alternation are able to assign their $\theta$-role to one argument position or two. The rest of the paper develops an account of this process.

\section{Periphrastic symmetric predicates and Role Exhaustion}
\label{periphrastic}

An interesting feature of the Split Theta Role Analysis is that it requires a predicate to assign the same $\theta$-role to two different arguments. This is generally prevented. Verbs do not usually come equipped with the ability to assign the same $\theta$-role to two different arguments. That verbs of this kind are generally forbidden is canonized in laws tailored to a variety of different frameworks. In \citet{Chomsky:1981}, it's called the Theta Criterion.
\begin{exe}
\raggedright
  \ex \label{ex:TC} Theta Criterion\\
  No $\theta$-role may be assigned by a verb to more than one argument position.
\end{exe}
We agree with \citet{Carlson:1984aa}, \citet{Dowty:1989}, \citet{Schein:1993}, and \citet{Williams:2015} that the Theta Criterion is a consequence of the meaning of predicates, and not a syntactic principle. That meanings are relevant is indicated by the fact that (\ref{ex:unique1}) doesn't entail~(\ref{ex:unique2}). (This argument comes from \citealt{Schein:1993}.)
\begin{exe}
\raggedright
  \ex \label{ex:unique}
  \begin{xlist}
    \ex \label{ex:unique1} Arjun and Aisha baked a cake.
    \ex \label{ex:unique2} Arjun baked a cake.
  \end{xlist}
\end{exe}
(\ref{ex:unique2}) describes an event that has Arjun as agent, and (\ref{ex:unique1}) describes the same event, but one where Arjun and Aisha are agent. We should expect that (\ref{ex:unique1}) entails (\ref{ex:unique2}), since both describe a baking-cake event with an Agent that includes Arjun. But (\ref{ex:unique1}) fails to entail (\ref{ex:unique2}) because (\ref{ex:unique1}) has a collective interpretation. It can describe a situation in which neither Arjun nor Aisha are the sole agents of the baking event, but instead collectively are. (Arjun sifts the flour, for instance, and Aisha cracks the eggs.) If we choose a predicate that doesn't have a collective interpretation, like \textit{sneeze}, the entailment does go through: (\ref{ex:unique3}) entails~(\ref{ex:unique4}).
\begin{exe}
\raggedright
  \ex \label{ex:unique3} Arjun and Aisha sneezed.
  \ex \label{ex:unique4} Arjun sneezed.
\end{exe}

But why does a collective interpretation of (\ref{ex:unique1}) not entail (\ref{ex:unique2})? Being the agent of the cake-baking event described by (\ref{ex:unique2}) must not be the same as participating as agent in a cake-baking. If, however, the agent relation requires that its argument refer to all those entities that are agents of the event(s) being described, then the event described by (\ref{ex:unique1}) is different from the event described by (\ref{ex:unique2}). If being an agent of an event means being the exclusive agent of that event, then (\ref{ex:unique1}) correctly fails to entail (\ref{ex:ex:unique2}).

To derive this, we propose that the denotation of the \textsc{agent} $\theta$-role has the exhaustivity requirement defined in (\ref{ex:exhaust}) associated with it. The denotation of agent is therefore (\ref{ex:uniqueth1}), and the denotations for $\theta$-roles generally are as~(\ref{ex:uniqueth2}) describes. (The name ``role exhaustion'' comes from \citealt[chapter 8.2, p.~165]{Williams:2015}.)
\begin{exe}
\raggedright
  \ex \label{ex:uniqueth} Role Exhaustion
  \begin{xlist}
    \ex \label{ex:exhaust} \textsc{$\theta$}_{X}($a$)($\epsilon$) = \textsc{$\theta$}($a$)($\epsilon$) $\wedge$ $\forall y$ [\textsc{$\theta$}($y$)($\epsilon$) $\rightarrow\ y \leq a$] 
    \ex \label{ex:uniqueth1} \denotes{agent} = $\lambda x\ \lambda \epsilon$ \textsc{agent}_{X}($x$)($\epsilon$)
    \ex \label{ex:uniqueth2} \denotes{$\theta$} = $\lambda x\ \lambda \epsilon$ \textsc{$\theta$}_{X}($x$)($\epsilon$)
  \end{xlist}
\end{exe}
Role Exhaustion causes (\ref{ex:unique2}) to describe a different event than (\ref{ex:unique1}) does when it is collective. It excludes those events in which there is someone other than Arjun participating in the agent relation. This not only explains the failure of entailment between (\ref{ex:unique1}) and (\ref{ex:unique2}) but it also takes a large step towards deriving the Theta Criterion, as  assigning the same $\theta$-role to two arguments would impose the restriction on each of them that they uniquely have that $\theta$-role.%
%
\footnote{Role Exhaustion would, unaided, allow violations of the Theta Criterion if the two arguments bearing the same $\theta$-role refer to the same entity. In principle, then, Role Exhaustion be satisfied by a verb that assigns the same $\theta$-role to two arguments that are necessarily covalued. We don't know of verbs like this. Perhaps this is too narrow a meaning for a language to develop a verb for.}%
%
\ We'll use Role Exhaustion in what follows to express the Theta Criterion, but there are surely other ways of deriving the Theta Criterion that are compatible with our analysis.

Verbs that participate in the argument splitting alternation have a way of assigning $\theta$-roles that circumvents Role Exhaustion. We believe that comitative constructions, like~(\ref{ex:com1}), provide a way of allowing one $\theta$-role to be assigned to two arguments. 
\begin{exe}
\raggedright
  \ex \label{ex:com1} Aisha ran with Arjun.
  \begin{xlist}
    \ex $\approx$ Aisha and Arjun are both agents of the same running event.
    \ex $\approx$ Aisha is the agent of the running event and Arjun accompanies Aisha.
  \end{xlist}
\end{exe}
The relation that \textit{with} establishes between \textit{Arjun} and \textit{Aisha} in (\ref{ex:com1}) includes one in which both \textit{Aisha} and \textit{Arjun} are agents of the running event. Role Exhaustion should prevent that interpretation, and so there must be some way in which the comitative overcomes that effect. We'll begin, then, with an analysis of comitatives and, once that's in hand, return to symmetric predicates.

\subsection{Comitative ``with''}

We start by considering how a \textit{with} phrase can be the predicate of a copular construction like (\ref{ex:withcop}). We suggest the denotation of \textit{with} is~(\ref{ex:withden}).
\begin{exe}
\raggedright
  \ex \label{ex:withcop} Aisha is with Arjun.
  \ex \label{ex:withden} \denotes{$\surd$with} = \parbox[t]{3in}{$\lambda P\ \lambda x\ \lambda y\ \lambda \epsilon$  $P$($x \oplus y$)($\epsilon$)}
  \ex \label{ex:withcopt}
  \small
  \begin{forest}
  [$\lambda \epsilon$ $R$(Arjun $\oplus$ Aisha)($\epsilon$)\\TP
    [DP [Aisha, roof]]
    [$\lambda 2\ \lambda \epsilon$ $R$(Arjun $\oplus$ 2)($\epsilon$) \\TP
      [T [is]]
      [$\lambda \epsilon$ $R$(Arjun $\oplus$ 2)($\epsilon$) \\PP
        [\textit{t_2} ]
        [$\lambda y\ \lambda \epsilon$ $R$(Arjun $\oplus y$)($\epsilon$) \\PP
          [P\\ (with) [$\lambda P\ \lambda x\ \lambda y\ \lambda \epsilon$  $P$($x \oplus y$)($\epsilon$)\\ $\surd$with] [$R$]]
          [DP [Arjun, roof]]
         ]
       ]
     ]
  ]
  \end{forest}
\end{exe}
As (\ref{ex:withcopt}) indicates, the denotation of (\ref{ex:withcop}) is a predicate that describes eventualities which the sum of Aisha and Arjun have the relation, $R$, to. $R$ is a free variable, whose value is influenced by context. In (\ref{ex:R}) are some illustrative contexts, and the accompanying value for $R$ that they favor.
\begin{exe}
\raggedright
  \ex \label{ex:R}
  \begin{xlist}
    \ex
    \begin{xlist}
    \exi{Q:} Where is Aisha?
    \exi{A:} She is with Arjun.\\ $R$ $\approx$ $\lambda x\ \lambda \epsilon$ \textsc{at}($x$)($\epsilon$) $\wedge$ \textsc{location}($\epsilon$)
    \end{xlist}
    \ex
    \begin{xlist}
      \exi{Q:} Who will dance together at the contest?
      \exi{A:} Aisha is with Arjun and I am with you.\\ $R$ $\approx$ $\lambda x\ \lambda \epsilon$ \textsc{participant}($x$)($\epsilon$) $\wedge$ \textsc{dance}($\epsilon$)
    \end{xlist}
    \ex 
    \begin{xlist}
      \exi{Q:} Is anyone else voting for the measure?
      \exi{A:} I'm with you!\\ $R$ $\approx$ $\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{vote}($\epsilon$)
    \end{xlist}
    \ex 
    \begin{xlist}
      \exi{Q:} Is Aisha single?
      \exi{A:} She is with Arjun.\\ $R$ $\approx$ $\lambda x\ \lambda \epsilon$ \textsc{participant}($x$)($\epsilon$) $\wedge$ \textsc{relationship}($\epsilon$)
    \end{xlist}
  \end{xlist}
\end{exe}
A key feature of this account is that \textit{with} forms a sum of the referents of its two arguments. This is the feature that will play the role of satisfying Role Exhaustion.

If this is the right denotation for \textit{with}, then we need to understand how that denotation can form comitatives. There is some superficial reason to think that comitatives are a kind of depictive. Depictives require that the state described by the depictive overlap temporally with the event of the verb the depictive combines with. In (\ref{ex:dep1}a), for instance, entails that Aisha is drunk contemporaneously with the running event she is the agent of. That is also true of the comitative in (\ref{ex:dep1}b); being accompanied by Arjun must be contemporaneous with the running event.
\begin{exe}
\raggedright
  \ex \label{ex:dep1} 
  \begin{xlist}
    \ex Aisha ran the marathon drunk.
    \ex Aisha ran the marathon with Arjun.
  \end{xlist}
\end{exe}
Moreover, depictives are sensitive to the event structure of the verb that they combine with. \citet[(6):~11]{Ardid-Gumiel:2001} argues, for instance, that an adjectival depictive must ``make reference to either a process (sub)event or transition.'' This makes depictives incapable of combining with non-process achievements, she argues. Examples are (\ref{ex:dep2}).
\begin{exe}
\raggedright
  \ex \label{ex:dep2}
  \begin{xlist}
    \ex[*]{Maria grasped the irony nervous.}
    \sn \textit{compare:} Maria grasped the gun nervous.
    \ex[*]{Maria recognized my car clean.}
    \sn \textit{compare:} Maria returned my car clean.
  \end{xlist}
  \hfill \citep[based on (7)-(8):~5]{Ardid-Gumiel:2001}\hfill\hspace*{.15in}
\end{exe}
We see the same restriction for comitatives.
\begin{exe}
\raggedright
  \ex \label{ex:com1}
  \begin{xlist}
    \ex[*]{Maria grapsed the irony with Pablo.}
    \sn \textit{compare:} Maria grasped the gun with Pablo.
    \ex[*]{Maria recognized my car with the bus.}
    \sn \textit{compare:} Maria returned my car with the bus.
  \end{xlist}
\end{exe}
We suggest, then, that comitatives can be analyzed as predicates formed from \textit{with}-phrases that are used as depictives.

Let's begin with an account of depictives formed from adjectives. Assume that adjectives describe states which their arguments hold, along the lines in (\ref{ex:nakedbare}).
\begin{exe}
\raggedright
  \ex \label{ex:nakedbare}
  \small
  \begin{forest}
  [$\lambda \epsilon$ \textsc{holder}(Smith)($\epsilon$) $\wedge$ \textsc{naked}($\epsilon$)
    [DP [Smith, roof] ]
    [$\lambda x\ \lambda \epsilon$ \textsc{holder}($x$)($\epsilon$) $\wedge$ \textsc{naked}($\epsilon$)\\ AP [naked, roof] ]
  ]
  \end{forest}
\end{exe}
In depictives, we'll assume there is a hidden morpheme that connects these state descriptions to the VP and imposes the temporal overlap and event structure conditions in the way that (\ref{ex:depictive}) indicates. (\ref{ex:depictiveill}) illustrates.
\begin{exe}
\raggedright
  \ex \label{ex:depictive} \denotes{dep} = $\lambda P\ \lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'\ P(x)(\epsilon')\ \wedge\ Q(x)(\epsilon)\ \wedge$ $\epsilon\ \circ \epsilon'$
  \ex \label{ex:depictiveill}
  \small
  \begin{forest}
      [$\lambda \epsilon\ \exists \epsilon'$ \textsc{holder_x}(Arjun)($\epsilon'$) $\wedge$ \textsc{naked}($\epsilon'$) $\wedge$ \\ \textsc{agent_x}(Smith)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$ $\epsilon\ \circ \epsilon'$\\VoiceP
        [DP [Arjun, roof] ]
        [$\lambda x\ \lambda \epsilon\ \exists \epsilon'$ \textsc{holder_x}($x$)($\epsilon'$) $\wedge$ \textsc{naked}($\epsilon'$) $\wedge$\\ \textsc{agent_x}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$ $\epsilon\ \circ \epsilon'$\\VoiceP
        [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) \\VoiceP
          [Voice [agent_x]]
          [VP [$\surd$run]]
         ]
         [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'$ \textsc{holder_x}($x$)($\epsilon'$) $\wedge$ \textsc{naked}($\epsilon'$) $\wedge$\\ $Q$($x$)($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$ \\DepP
          [Dep ]
          [$\lambda x\ \lambda \epsilon$ \textsc{holder}($x$)($\epsilon$) $\wedge$ \textsc{naked}($\epsilon$) \\AP [naked, roof]]
         ]
       ]
     ]
  \end{forest}
\end{exe}
We code the temporal and event conditions with ``$\circ$.''

A depictive that targets an object has the syntax and semantics indicated in~(\ref{ex:depobj1}).
\begin{exe}
\raggedright
  \ex \label{ex:depobj1}
  \small
  \begin{forest}
  [VoiceP
    [DP [Arjun, roof]]
    [VoiceP
      [Voice [agent_x]]
      [$\lambda \epsilon\ \exists \epsilon'$ \textsc{holder_x}(Aisha)($\epsilon'$) $\wedge$ \textsc{happy}($\epsilon'$) $\wedge$\\ \textsc{patient_x}(Aisha)($\epsilon$) $\wedge$ \textsc{see}($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$\\VP
        [DP [Aisha, roof]]
        [$\lambda x\ \lambda \epsilon\ \exists \epsilon'$ \textsc{holder_x}($x$)($\epsilon'$) $\wedge$ \textsc{happy}($\epsilon'$) $\wedge$\\ \textsc{patient_x}($x$)($\epsilon$) $\wedge$ \textsc{see}($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$\\VP
          [$\lambda y\ \lambda \epsilon$ \textsc{patient_x}($y$)($\epsilon$) $\wedge$ \textsc{see}($\epsilon$) \\VP [V [$\surd$see]]]
          [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'$ \textsc{holder_x}($x$)($\epsilon'$) $\wedge$ \textsc{happy}($\epsilon'$) $\wedge$\\ $Q(x)(\epsilon)$ $\wedge$ $\epsilon \circ \epsilon'$  \\DepP
            [Dep ]
            [AP [happy, roof]]
          ]
         ]
       ]
     ]
  ]
  \end{forest}
\end{exe}

If we've correctly modeled the semantics of \textit{with}-phrases, we should expect them to be able to be depictives, with the syntax and semantics illustrated by~(\ref{ex:withdep1}) and~(\ref{ex:withdep2}).
\begin{exe}
\raggedright
  \ex \label{ex:withdep1}
  % \small
  \begin{forest}
  [$\lambda \epsilon\ \exists \epsilon'$ $R(\text{Aisha} \oplus \text{Arjun})(\epsilon')$\\ $\wedge$ \textsc{agent_x}(Arjun)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$\\VoiceP
  [DP [Arjun, roof] ]
      [$\lambda x\ \lambda \epsilon\ \exists \epsilon'$ $R(\text{Aisha} \oplus y)(\epsilon')$\\ $\wedge$ \textsc{agent_x}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$\\VoiceP
    [$\lambda x\ \lambda \epsilon$ \textsc{agent_x}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) \\VoiceP
        [Voice [agent]]
        [VP [$\surd$run] ]
       ]
       [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'$ $R(\text{Aisha} \oplus y)(\epsilon')$\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ $\epsilon \circ \epsilon'$\\DepP
       [Dep]
      [$\lambda y\ \lambda \epsilon$  $R(\text{Aisha} \oplus y)(\epsilon)$ \\PP [with Aisha, roof] ]
       ]
     ]
  ]
  \end{forest}
  \ex \label{ex:withdep2}
  \begin{forest}
  [VoiceP
    [DP [Maria, roof]]
    [VoiceP
      [Voice [agent_x]]
      [$\lambda \epsilon\ \exists \epsilon'\ R(\text{bus} \oplus \text{car})(\epsilon')$ $\wedge$\\ \textsc{patient_x}(car)($\epsilon$) $\wedge$ \textsc{return}($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$ \\VP
        [DP [my car, roof]]
        [$\lambda x\ \lambda \epsilon\ \exists \epsilon'\ R(\text{bus} \oplus x)(\epsilon')$ $\wedge$\\ \textsc{patient_x}($x$)($\epsilon$) $\wedge$ \textsc{return}($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$ \\VP
          [$\lambda y\ \lambda \epsilon$ \textsc{patient_x} $\wedge$ \textsc{return}($\epsilon$) \\V [$\surd$return]]
          [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'\ R(\text{bus} \oplus x)(\epsilon)$\\DepP
            [Dep ]
            [PP [with the bus, roof]]
           ]
         ]
       ]
     ]
  ]
  \end{forest}
\end{exe}
If we let the value of $R$ be paraphrased by ``accompanied by,'' then the meanings delivered in these examples are roughly those paraphrased in~(\ref{ex:withdepm}).
\begin{exe}
\raggedright
  \ex \label{ex:withdepm}
  \begin{xlist}
    \ex Arjun ran while accompanied by Aisha.
    \ex Maria returned my car while it was accompanied by the bus
  \end{xlist}
\end{exe}

Consider what happens if $R$ gets the value that VoiceP or V have in these examples. This would produce for (\ref{ex:withdep1}) and (\ref{ex:withdep2}) the meanings indicated in~(\ref{ex:withdepms}).
\begin{exe}
\raggedright
  \ex \label{ex:withdepms}
  \begin{xlist}
    \ex $\lambda \epsilon\ \exists \epsilon'$ \textsc{agent_x}$(\text{Aisha} \oplus \text{Arjun})(\epsilon') \wedge \textsc{run}(\epsilon')$\\ $\wedge$ \textsc{agent_x}(Arjun)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$
    \sn $\approx$ Arjun ran while Aisha and Arjun ran
    \ex $\lambda \epsilon\ \exists \epsilon'\ \textsc{patient_x}(\text{bus} \oplus \text{car})(\epsilon') \wedge \textsc{return}(\epsilon')$ $\wedge$\\ \textsc{patient_x}(car)($\epsilon$) $\wedge$ \textsc{return}($\epsilon$) $\wedge$ $\epsilon \circ \epsilon'$
    \sn $\approx$ Maria returned my car while returning my car and the bus
  \end{xlist}
\end{exe}
These denotations informally say that the events of Arjun-running and car-returning that the verbs describe overlap with an event of Arjun$\oplus$Aisha-running and car$\oplus$bus-returning that the \textit{with}-phrase describes. Note that Role Exhaustion requires that these events be different---one has a singular argument and the other has a plural argument---but the depictive causes them to overlap. We can't see how this meaning would be used to describe situations in which there is one event of running that involves both Arjun and Aisha and one event of returning that involves both my car and the bus. Of the many meanings that a \textit{with}-phrase can have when it is used as a depictive, one of those is indistinguishable from a symmetric one. Switching \textit{Arjun} and \textit{Aisha} in (\ref{ex:withdepms}a) gives a nearly equivalent meaning, as does switching \textit{my car} and \textit{the bus} in~(\ref{ex:withdepms}b).

On this construal, the comitative comes close to being a paraphrastic symmetric predicate. Indeed, many of the predicates that are offered as examples of symmetric predicates involve \textit{with}. Interestingly, these cases don't have the same range of meanings that \textit{with} otherwise permits. Instead, in these cases, \textit{with} only gives rise to a periphrastic symmetric interpretation. We suggest the denotation of \textit{with} has been reanalyzed into one that requires that the free variable it introduces be provided by the verbal projection it attaches to. These are no longer depictives, but instead cases where \textit{with} can combine directly with a predicate of the right meaning. The denotation we suggest is (\ref{ex:withsym}).
\begin{exe}
\raggedright
  \ex \label{ex:withsym} \denotes{with} = $\lambda x\ \lambda y\ \lambda P\ \lambda \epsilon\ P(x \oplus y)(\epsilon)$
\end{exe}
(\ref{ex:withsym1}) and (\ref{ex:withsym2}) illustrate how this works.
\pagebreak
\begin{exe}
\raggedright
  \ex \label{ex:withsym1}\ \\[8pt]

  \hspace*{-40pt}
  \small
  \begin{forest}
  [$\exists \epsilon\ \textsc{participant_x}(\text{mine} \oplus \text{your name})(\epsilon) \wedge \textsc{rhyme}(\epsilon)$\\TP
    [DP [your name, roof, name=binder]]
    [TP
    [T [past]]
    [$\lambda \epsilon\ \textsc{participant_x}(\text{mine} \oplus 2)(\epsilon) \wedge \textsc{rhyme}(\epsilon)$\\VoiceP
    [$\lambda y\ \lambda \epsilon\ \textsc{participant_x}(y)(\epsilon) \wedge \textsc{rhyme}(\epsilon)$\\VoiceP
      [Voice [participant_x]]
      [VP [V [rhyme]]
       ]
     ]
    [$\lambda P\ \lambda \epsilon P(\text{mine} \oplus 2)(\epsilon)$ \\PP
    [t_2, name=trace]
    [$\lambda y\ \lambda P\ \lambda \epsilon P(\text{mine} \oplus y)(\epsilon)$ \\PP
    [$\lambda x\ \lambda y\ \lambda P\ \lambda \epsilon P(x \oplus y)(\epsilon)$ \\P [with]] 
    [DP [mine, roof]]
    ]
  ]
  ]]]
  \draw[->,>=stealth', thin, gray] (trace) to[out=south west,in=south,looseness=1] node[pos=0.75,xshift=-10mm]{} (binder);
  \end{forest}
  \ex \label{ex:withsym2}
  \hspace*{-40pt}
  \small
  \begin{forest}
  [VoiceP
    [DP [she, roof]]
    [VoiceP
      [Voice [agent_x]]
      [$\lambda \epsilon$ $\textsc{patient_x}(\text{menthol} \oplus \text{camphor}) \wedge \textsc{mix}(\epsilon)$ \\VP
        [DP [camphor, roof, name=binder]]
        [$\lambda 2\ \lambda \epsilon$ $\textsc{patient_x}(\text{menthol} \oplus 2) \wedge \textsc{mix}(\epsilon)$ \\VP
          [$\lambda y\ \lambda \epsilon$ \textsc{patient}($y$)($\epsilon$) $\wedge$ \textsc{mix}($\epsilon$) \\V [$\surd$mix]]
          [$\lambda P\ P(\text{menthol} \oplus 2)(\epsilon)$ \\PP
            [t_2, name=trace ]
            [$\lambda x\ \lambda P\ P(\text{menthol} \oplus x)(\epsilon)$ \\PP
              [P [with]]
              [DP [menthol, roof]]
             ]
           ]
         ]
       ]
     ]
  ]
  \draw[->,>=stealth', thin, gray] (trace) to[out=south west,in=south,looseness=1] node[pos=0.75,xshift=-10mm]{} (binder);
  \end{forest}
\end{exe}
Note that in these cases, the arguments that are in a symmetric relationship are not arguments of the verb. They are instead, arguments of \textit{with}. One of those arguments has moved, presumably for Case reasons. The $\theta$-roles that the verbs introduce end up assigned to the sum formed from the two arguments. This what \textit{with} does. Because \textit{with} causes the $\theta$-role to be assigned to the sum of the two arguments that \textit{with} combines with, Role Exhaustion is satisfied.

\subsection{Building the symmetric verb}

We speculate that symmetric predicates that don't involve the word \textit{with} are built from a syntax that nonetheless contains \denotes{$\surd$with}. That syntax puts the denotation of the verbal root into \textit{$\surd$with}.  (\ref{ex:symmfintrans}) and (\ref{ex:symmfinditrans}) illustrate. We give both frames for these verbs, to illustrate how the $aP$ $\Leftrightarrow$ $bPc$ alternation is modeled.
\begin{exe}
\raggedright
  \ex \label{ex:symmfintrans} $bPc$ frame:\\[8pt]
  % \small
  \begin{forest}
  [$\lambda \epsilon\textsc{patient_x}(\text{Aisha} \oplus \text{Arjun})(\epsilon) \wedge \textsc{date}(\epsilon)$\\VP
    [DP [Arjun, roof]]
    [$\lambda y\ \lambda \epsilon \textsc{patient_x}(\text{Aisha} \oplus y)(\epsilon) \wedge \textsc{date}(\epsilon)$\\VP
      [$\lambda x\ \lambda y\ \lambda \epsilon \textsc{patient_x}(x \oplus y)(\epsilon) \wedge \textsc{date}(\epsilon)$\\V\\(date) 
        [$\lambda P\ \lambda x\ \lambda y\ \lambda \epsilon\ P(x \oplus y)(\epsilon)$ \\$\surd$with ]
        [$\lambda x\ \textsc{patient_x}(x)(\epsilon) \wedge \textsc{date}(\epsilon)$\\$\surd$date ]
      ]
      [DP [Aisha, roof]]
     ]
  ]
  \end{forest}\\
  \normalsize \sn \textit{=Arjun dated Aisha.}
  \bigskip

  \normalsize \ex $aP$ frame:\\[8pt]
  % \small
  \begin{forest}
  [$\lambda \epsilon$ \textsc{agent}_{X}(Aisha $\oplus$ Arjun)($\epsilon$) $\wedge$ \textsc{date}($\epsilon$) \\TP
    [DP [Aisha and Arjun, roof, name=binder]]
    [TP
    [T]
    [$\lambda \epsilon$ \textsc{patient}_{x}(Aisha and Arjun)($\epsilon$) $\wedge$ \textsc{date}($\epsilon$) \\VP
    [V [$\surd$date]
      [t, name=trace]
      ]
     ]
  ]]
  \draw[->,>=stealth', thin, gray] (trace) to[out=south west,in=south,looseness=1] node[pos=0.75,xshift=-10mm]{} (binder);
  \end{forest}\\
    \normalsize \sn \textit{= Aisha and Arjun dated}
\pagebreak
   \ex \label{ex:symmfinditrans} $bPc$ frame:\\[8pt]
  % \small
  % \hspace*{-40pt}
\begin{forest}
    [$\lambda \epsilon$ \textsc{agent}_{X}(she)($\epsilon$) $\wedge$ \textsc{theme}_{X}(you $\oplus$ me)($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$) \\VoiceP
      [DP [she, roof]]
      [$\lambda x\ \lambda \epsilon$ \textsc{agent}_{X}($x$)($\epsilon$) $\wedge$ \textsc{theme}_{X}(you $\oplus$ me)($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$) \\VoiceP
        [Voice [agent]]
        [$\lambda \epsilon$ \textsc{theme}_{X}(you $\oplus$ me)($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$)\\VP
          [$\lambda y\ \lambda \epsilon$ \textsc{theme}_{X}(you $\oplus\ y)$($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$)\\VP
          [$\lambda x\ \lambda y\ \lambda \epsilon$ \textsc{theme}_{X}$(x \oplus\ y)$($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$)\\V\\ (introduce)
            [$\lambda z\ \lambda \epsilon$ \textsc{theme}_{X}($z$)($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$)\\V [$\surd$introduce]]
            [$\lambda P\ \lambda x\ \lambda y\ \lambda \epsilon$ $P(x \oplus\ y)$($\epsilon$)\\ $\surd$with ]
           ]
          [DP [you, roof]]
         ]
         [PP [to me, roof]]
       ]
     ]
   ]
\end{forest}\\[15pt]
\sn \textit{= She introduced you to me.}
\pagebreak

    \ex $aP$ frame:\\[8pt]
    % \small
    \begin{forest}
    [$\lambda \epsilon$ \textsc{agent}_{X}(she)($\epsilon$) $\wedge$ \textsc{theme}_{X}(us)($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$) \\VoiceP
      [DP [she, roof]]
      [$\lambda x\ \lambda \epsilon$ \textsc{agent}_{X}($x$)($\epsilon$) $\wedge$ \textsc{theme}_{X}(us)($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$) \\VoiceP
        [Voice [agent]]
        [$\lambda \epsilon$ \textsc{theme}_{X}(us)($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$) \\VP
          [$\lambda x\ \lambda \epsilon$ \textsc{theme}_{X}($x$)($\epsilon$) $\wedge$ \textsc{introduce}($\epsilon$) \\V [$\surd$introduce]]
          [DP [us, roof]]
         ]
       ]
    ]
    \end{forest}\\
    \normalsize \textit{= She introduced us.}
\end{exe}
Note that we take \textit{to} to be semantically vacuous.



%References
\printbibliography[title={\sffamily References}]

\end{document}

We'll treat comitatives as sorts of depictives. They describe states which temporally overlap the event described by the verb. First, let's unveil a theory of depictives. We'll assume that adjectives describe states which their arguments hold. So:
\begin{exe}
\raggedright
  \ex \label{ex:nakedbare}
  \small
  \begin{forest}
  [$\lambda \epsilon$ \textsc{holder}(Smith)($\epsilon$) $\wedge$ \textsc{naked}($\epsilon$)
    [DP [Smith, roof] ]
    [$\lambda x\ \lambda \epsilon$ \textsc{holder}($x$)($\epsilon$) $\wedge$ \textsc{naked}($\epsilon$)\\ AP [naked, roof] ]
  ]
  \end{forest}
\end{exe}
In depictives, we'll assume there is a hidden morpheme that connects these state descriptions to the VP and imposes the temporal overlap condition.
\begin{exe}
\raggedright
  \ex \label{ex:depictive} \denotes{dep} = $\lambda P\ \lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'\ P(x)(\epsilon')\ \wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)
  \ex
  \small
  \small
  \begin{forest}
      [vP
        [DP [Smith, roof] ]
        [$\lambda x\ \lambda \epsilon\ \exists \epsilon'$ \textsc{holder}($x$)($\epsilon'$) $\wedge$ \textsc{naked}($\epsilon'$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$) $\wedge$\\ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) \\vP
        [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) \\vP
          [v [agent]]
          [VP [run]]
         ]
         [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'$ \textsc{holder}($x$)($\epsilon'$) $\wedge$ \textsc{naked}($\epsilon'$) $\wedge$\\ $Q$($x$)($\epsilon$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$) \\DepP
          [Dep ]
          [$\lambda x\ \lambda \epsilon$ \textsc{holder}($x$)($\epsilon$) $\wedge$ \textsc{naked}($\epsilon$) \\AP [naked, roof]]
         ]
       ]
     ]
  \end{forest}
\end{exe}

So, to understand comitatives, we need to give an account of the kind of state they denote. Maybe we can converge on that by considering sentences like:
\begin{exe}
\raggedright
  \ex \label{ex:combas}
  \begin{xlist}
    \ex She is with you.
    \ex I saw you with her.
  \end{xlist}
\end{exe}
Intuitively, we want these expressions to denote states which are true if she and you are a group. If these constructions are related to expressions like (\ref{ex:russian}), grammatical in some languages, then we want that group to be unbreakable.
\begin{exe}
\raggedright
  \ex \label{ex:russian}
  She with you arrived.
\end{exe}
What we want to do in (\ref{ex:russian}) is make it impossible for there to be two unrelated arrivals: one by you and one by her. We have the additional need to make "she with you" refer to a plurality---that's not a requirement for our semantics in English because examples like (\ref{ex:russian}) don't arise. I'll not strive to get that result, but I will strive to capture the anti-distributive nature of these expressions. What we'll want is for the \emph{with} phrases in (\ref{ex:combas}) to denote eventualities in which the two arguments are parts of. If we want to put the Russian facts here too (we might not) we can add that if they are part of an event that \emph{with} describes, they are parts of all subevents. Here's a stab at it.
\begin{exe}
\raggedright
  \ex \label{ex:denwith}
  \denotes{with} =  \parbox[t]{3in}{$\lambda x\ \lambda y\ \lambda \epsilon$  $P(\epsilon) \wedge$ $H$($y$)($\epsilon$) $\wedge$ $H$($x$)($\epsilon$)\\ ( $\wedge$ $\forall \epsilon',\epsilon''$ [$H$($x$)($\epsilon',\epsilon'') \wedge$ $H$($y$)($\epsilon',\epsilon''$)] $\rightarrow$ $\epsilon' = \epsilon''$)}
\end{exe}
The $P$ and $H$ are free variables. Their values will be supplied by the context. What (\ref{ex:denwith}) says is that the two individuals that \emph{with} combines are related in the same way to an event that is $H$. In parentheses is the additional, Russian, condition that $H$ cannot relate these two individuals to different eventualities. I'll leave whether this is part of the denotation or not open. The result of combining two individuals with \emph{with}, then, is a predicate that describes eventualities in which those individuals form a group by some contextually salient~$P$. A demonstration:
\begin{exe}
\raggedright
\ex \label{ex:withsimptree}
% \small
\begin{forest}
[$\lambda \epsilon$  $P(\epsilon) \wedge$ $H$(Smith)($\epsilon$) $\wedge$ $H$(Jones)($\epsilon$)\\PP
  [DP [Smith, roof] ]
  [$\lambda y\ \lambda \epsilon$  $P(\epsilon) \wedge$ $H$($y$)($\epsilon$) $\wedge$ $H$(Jones)($\epsilon$)\\PP
    [$\lambda x\ \lambda y\ \lambda \epsilon$  $P(\epsilon) \wedge$ $H$($y$)($\epsilon$) $\wedge$ $H$($x$)($\epsilon$)\\P [with] ]
    [DP [Jones, roof] ]
   ]
]
\end{forest}
\end{exe}

Okay, let's see how this will work when the \emph{with}-phrase is a depictive.
\begin{exe}
\raggedright
  \ex
  % \small
  \begin{forest}
  [$\lambda \epsilon\ \exists \epsilon'$ $P(\epsilon')$ $\wedge$ $H$(Smith)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$)\\ $\wedge$ \textsc{agent}(Smith)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\vP
  [DP [Smith, roof] ]
      [$\lambda x\ \lambda \epsilon\ \exists \epsilon'$ $P(\epsilon')$ $\wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$)\\ $\wedge$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\vP
    [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) \\vP
        [v [agent]]
        [VP [run] ]
       ]
       [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'$ $P(\epsilon')$ $\wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$)\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\DepP
       [$\lambda R\ \lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'\ R(x)(\epsilon')$\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\Dep]
      [$\lambda y\ \lambda \epsilon$  $P(\epsilon) \wedge$ $H$($y$)($\epsilon$) $\wedge$ $H$(Jones)($\epsilon$)\\PP [with Jones, roof] ]
       ]
     ]
  ]
  \end{forest}
\end{exe}
If this context provides the denotation of the VP, \emph{run}, as a salient antecedent for $P$, then we have what we want (I think).
\pagebreak

Let's add \emph{together} and see what happens. We've talked about two possible syntaxes: one with \emph{together} attached to vP. Let's look at that one first.
\begin{exe}
  \ex \label{ex:togwith}
  % \small
  \begin{forest}
        [$\lambda \epsilon\ \exists \epsilon'$ $P(\epsilon')$ $\wedge$ $H$(Smith)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$) $\wedge$ \textsc{agent}(Smith)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$\\ $\forall \epsilon'$ {[}\textsc{agent}(Smith)($\epsilon'$) $\wedge$ \textsc{run}($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon$ $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\vP
        [DP [Smith, roof]]
          [$\lambda x\ \lambda \epsilon\ \exists \epsilon'$ $P(\epsilon')$ $\wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$) $\wedge$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$\\ $\forall \epsilon'$ {[}\textsc{agent}($x$)($\epsilon'$) $\wedge$ \textsc{run}($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon$ $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\vP
          [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$\\ $\forall \epsilon'$ {[}\textsc{agent}($x$)($\epsilon'$) $\wedge$ \textsc{run}($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon$ \\vP
              [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$)\\vP 
                [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) \\v [agent]]
                [$\lambda \epsilon$ \textsc{run}($\epsilon$)\\VP [run, roof] ]
              ]
              [together]
             ]
             [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'$ $P(\epsilon')$ $\wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$)\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\DepP
             [Dep]
            [PP [with Jones, roof] ]]
           ]]
  \end{forest}
\end{exe}
The denotation of \emph{together} is going to have to introduce a presupposition that the event it describes be ``plural.'' That is, it's going to require that the VP \emph{run} have two agents. That can be satisfied here only if $H$ is given the value that \denotes{vP} has. This will force Smith and Jones to be the agents of the running eventuality. This is shown on the following page. (Note that $P$ has to be \emph{run}).
\pagebreak
\begin{exe}
\raggedright
  \ex \label{ex:togwith2}
  % \small
  \begin{forest}
    [$\lambda \epsilon\ \exists \epsilon'$ \textsc{run}$(\epsilon')$ $\wedge$ \textsc{agent}(Smith)($\epsilon'$) $\wedge$ \textsc{agent}(Jones)($\epsilon'$) $\wedge$ \textsc{agent}(Smith)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$\\ $\forall \epsilon'$ {[}\textsc{agent}(Smith)($\epsilon'$) $\wedge$ \textsc{run}($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon$ $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\vP
    [DP [Smith, roof]]
      [$\lambda x\ \lambda \epsilon\ \exists \epsilon'$ $P(\epsilon')$ $\wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$) $\wedge$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$\\ $\forall \epsilon'$ {[}\textsc{agent}($x$)($\epsilon'$) $\wedge$ \textsc{run}($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon$ $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\vP
      [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$) $\wedge$\\ $\forall \epsilon'$ {[}\textsc{agent}($x$)($\epsilon'$) $\wedge$ \textsc{run}($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon$ \\vP
          [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{run}($\epsilon$)\\vP 
            [$\lambda x\ \lambda \epsilon$ \textsc{agent}($x$)($\epsilon$) \\v [agent]]
            [$\lambda \epsilon$ \textsc{run}($\epsilon$)\\VP [run, roof] ]
          ]
          [together]
         ]
         [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'$ $P(\epsilon')$ $\wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$)\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$)\\DepP
         [Dep]
        [PP [with Jones, roof] ]]
       ]]
\end{forest}
\end{exe}
This is very close to what we want. Does it force Jones to be ``together''? Let's now look at what happens if \emph{together} forms a constituent with the \emph{with}-phrase.
\pagebreak
\begin{exe}
\raggedright

  \ex \label{ex:togw}
  % \small
  \begin{forest}
  [$\lambda \epsilon\ \exists \epsilon''$ $P(\epsilon'') \wedge$ $H$(Smith)($\epsilon''$) $\wedge$ $H$(Jones)($\epsilon''$) $\wedge\ \forall \epsilon'$ {[}$P(\epsilon') \wedge$ $H$(Smith)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon''$\\ $\wedge$ \textsc{run}($\epsilon$) $\wedge$ \textsc{agent}(Smith)($\epsilon$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon''$)\\vP
  [DP [Smith, roof]]
  [$\lambda x\ \lambda \epsilon\ \exists \epsilon''$ $P(\epsilon'') \wedge$ $H$($x$)($\epsilon''$) $\wedge$ $H$(Jones)($\epsilon''$) $\wedge\ \forall \epsilon'$ {[}$P(\epsilon') \wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon''$\\ $\wedge$ \textsc{run}($\epsilon$) $\wedge$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon''$)\\vP
    [$\lambda x\ \lambda \epsilon$ \textsc{run}($\epsilon$) $\wedge$ \textsc{agent}($x$)($\epsilon$) \\vP [run, roof]]
      [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon''$ $P(\epsilon'') \wedge$ $H$($x$)($\epsilon''$) $\wedge$ $H$(Jones)($\epsilon''$) $\wedge\ \forall \epsilon'$ {[}$P(\epsilon') \wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon''$\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon''$)\\DepP
      [$\lambda R\ \lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon''\ R(x)(\epsilon'')$\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon''$)\\Dep]
      [$\lambda x\ \lambda \epsilon$ $P(\epsilon) \wedge$ $H$($x$)($\epsilon$) $\wedge$ $H$(Jones)($\epsilon$) $\wedge$\\ $\forall \epsilon'$ {[}$P(\epsilon') \wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon$\\PP
        [together ]
        [$\lambda y\ \lambda \epsilon$  $P(\epsilon) \wedge$ $H$($y$)($\epsilon$) $\wedge$ $H$(Jones)($\epsilon$)\\PP
          [P [with]]
          [DP [Jones, roof] ]
         ]
       ]]
    ]]
  \end{forest}
\end{exe}
And, as before, let $H$ and $P$ be the denotations that are assigned to the vP and VP containing agent+run. We get:
\pagebreak
\begin{exe}
  \raggedright
  
    \ex \label{ex:togw2}
    % \small
    \begin{forest}
      [$\lambda \epsilon\ \exists \epsilon''$ \textsc{run}$(\epsilon'') \wedge$ \textsc{agent}(Smith)($\epsilon''$) $\wedge$ \textsc{agent}(Jones)($\epsilon''$) $\wedge$\\ $\forall \epsilon'$ {[}\textsc{run}$(\epsilon') \wedge$ \textsc{agent}(Smith)($\epsilon'$) $\wedge$ \textsc{agent}(Jones)($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon''$\\ $\wedge$ \textsc{run}($\epsilon$) $\wedge$ \textsc{agent}(Smith)($\epsilon$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon''$)\\vP
      [DP [Smith, roof]]
      [$\lambda x\ \lambda \epsilon\ \exists \epsilon''$ $P(\epsilon'') \wedge$ $H$($x$)($\epsilon''$) $\wedge$ $H$(Jones)($\epsilon''$) $\wedge$\\ $\forall \epsilon'$ {[}$P(\epsilon') \wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon''$\\ $\wedge$ \textsc{run}($\epsilon$) $\wedge$ \textsc{agent}($x$)($\epsilon$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon''$)\\vP
        [$\lambda x\ \lambda \epsilon$ \textsc{run}($\epsilon$) $\wedge$ \textsc{agent}($x$)($\epsilon$) \\vP [run, roof]]
          [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon''$ $P(\epsilon'') \wedge$ $H$($x$)($\epsilon''$) $\wedge$ $H$(Jones)($\epsilon''$) $\wedge$\\ $\forall \epsilon'$ {[}$P(\epsilon') \wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon''$\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon''$)\\DepP
          [$\lambda R\ \lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon''\ R(x)(\epsilon'')$\\ $\wedge\ Q(x)(\epsilon)\ \wedge$ \textsc{overlap}($\epsilon$)($\epsilon''$)\\Dep]
          [$\lambda x\ \lambda \epsilon$ $P(\epsilon) \wedge$ $H$($x$)($\epsilon$) $\wedge$ $H$(Jones)($\epsilon$) $\wedge$\\ $\forall \epsilon'$ {[}$P(\epsilon') \wedge$ $H$($x$)($\epsilon'$) $\wedge$ $H$(Jones)($\epsilon'$){]} $\rightarrow$ $\epsilon' < \epsilon$\\PP
            [together ]
            [$\lambda y\ \lambda \epsilon$  $P(\epsilon) \wedge$ $H$($y$)($\epsilon$) $\wedge$ $H$(Jones)($\epsilon$)\\PP
              [P [with]]
              [DP [Jones, roof] ]
             ]
           ]]
        ]]
      \end{forest}
  \end{exe}
\pagebreak
\begin{exe}
\raggedright
  \ex \label{ex:dep2}
  \begin{forest}
  [TP
    [DP^2 [she, roof]]
    [TP
      [T [past]]
      [vP
        [\emph{t_2} ]
        [vP
          [v [agent]]
          [VP
            [DP [Smith, roof]]
            [$\lambda x\ \lambda \epsilon\ \exists \epsilon'$ \textsc{holder}($x$)($\epsilon'$) $\wedge$ \textsc{drunk}($\epsilon'$) $\wedge$ \textsc{patient}($x$)($\epsilon$) $\wedge$ \textsc{kiss}($\epsilon$) $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$) \\VP
              [$\lambda x\ \lambda \epsilon$ \textsc{patient}($x$)($\epsilon$) $\wedge$ \textsc{kiss}($\epsilon$) \\VP [$\surd$kiss] ]
              [$\lambda Q\ \lambda x\ \lambda \epsilon\ \exists \epsilon'$ \textsc{holder}($x$)($\epsilon'$) $\wedge$ \textsc{drunk}($\epsilon'$) $\wedge$ $Q(x)(\epsilon)$ $\wedge$ \textsc{overlap}($\epsilon$)($\epsilon'$) \\DepP
                [Dep ]
                [$\lambda x\ \lambda \epsilon$ \textsc{holder}($x$)($\epsilon$) $\wedge$ \textsc{drunk}($\epsilon$) \\AP [drunk, roof] ]
              ]
             ]
           ]
         ]
       ]
     ]
  ]
  \end{forest}
\end{exe}
Maybe this is what we want too?

temporal overlap:

Aisha wrote the abstract in a funk./in her pajamas
== Aisha was in a funk when she wrote the abstract
=/= Aisha was writing the abstract when she was in a funk.

Aisha wrote the abstract with Arjun.
== they coauthored the abstract.
== Aisha wrote it with Arjun's guidance 
=?= Aisha wrote i


Aisha recognized the speaker (together) with Arjun
== They recognized speaker

?Aisha recognized the speaker in a funk.



``when reciprocal predicates show this equivalence, we refer to them as plain reciprocals'':
(4) Sue and Dan dated <==> Sue dated Dan (Dan dated Sue)
p. 3

P1. Meanings of symmetric predicates are logically derived from the collective meanings of their reciprocal alternates. (p.)

"To account for this pattern, it is proposed that the basic lexical meaning of symmetric binary predicates in English is unary-collective." (p. 4)

``symmetry is not an accidental semantic feature of binary predicates, but appears by virtue of their underlying collectivity.'' (p. 4)

Plain Reciprocity
for all x,y in E, such that x=\=y:P(X+y) <==> R(x,y) and R(y,x) (p. 5, (7))

 Reciprocity-symmetry Generalization: A reciprocal alternation between a unary collective predicate P and a binary R is \uline{plain} if and only if R is truth-conditionally symmetric. ((18), p. 11)

  ``...we logically derive the meaning of the binary construction from the collective meaning.'' (p. 14)

p. 24:
  A and B are in love ==> A is in love with B and B is in love with A, but A is in love with B and B is in love with A =\=> A&B are in love. ("talking to" is similar?)
  -- thought: could this be what happens with stative predicates that are like "hug"?

p. 27
Winter suggests that all these ``hug'' like examples obey this rule: P(x+y) ==> R(x,y) or R(y,x).

 p. 29: ``...transitive verbs without reciprocal alternates individuate single events.'' Sue pushed Dan and Dan pushed Sue ==> two pushes.

 /Users/kbj/Library/CloudStorage/Dropbox/ellipsis-and-symmetry/constructedsym/ConstructedPaper/constructedsym.tex